Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-08 PaperVictor.tex
Revise parte experimental

Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation is \notaV{Quite "will be"} forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
withinin a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses are \notaV{Modifique "of is"} quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a \notaV{Quite "some chosen"} nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.
\notaV{Se modifico la oracion "An alternative is to stack BM's, such that their PBG
overlap each other, resulting in a wider high-reflection band"}. 
\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
  que no son periódicos, tal vez 'brecha prohibida' no es un buen
  término. Más bien, queremos hablar del ancho de banda del espejo,
  i.e., la región en que es buen reflector.}

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de
  aquí, pues lo discutes abajo:(gravimetrically obtained)}, using
current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$,
respectively. However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, with
corresponding
porosities of 51\% and 76\%, respectively. The porosity was calibrated
\notaL{Creo que no muestras curvas de calibración: calibration curves were
acquired} through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions applying a constant
current for a time \notaL{cuánto tiempo para la calibración?}  and were weighed to
obtain their mass $m_i$
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to obtain
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.
The etching
rate of PS was obtained by synthetizing single layers under similar
conditions and measuring their thicknesses through Scanning Electron
Microscopy (SEM). Absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident
angles $\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$,
$40^{\circ }$, $50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

>>>>

Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation is \notaV{Quite "will be"} forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses are \notaV{Modifique "of is"} quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a \notaV{Quite "some chosen"} nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.
\notaV{Se modifico la oracion "An alternative is to stack BM's, such that their PBG
overlap each other, resulting in a wider high-reflection band"}. 
\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
  que no son periódicos, tal vez 'brecha prohibida' no es un buen
  término. Más bien, queremos hablar del ancho de banda del espejo,
  i.e., la región en que es buen reflector.}

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
\notaV{Se omite "With this electrolyte, the minimum and maximum porosities that can be obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de   aquí, pues lo discutes abajo:(gravimetrically obtained)}, using current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$, respectively.} 
However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, 
with corresponding porosities of 51\% and 76\%, respectively.
\notaV{Se reescribe "The porosity was calibrated \notaL{Creo que no 
muestras curvas de calibración: calibration curves were acquired}
through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions applying a constant
current for a time \notaL{cuánto tiempo para la calibración?} and
were weighed to obtain their mass $m_i$ before ($m_{1}$) and after 
($m_{2}$) the electrochemical attack, and after dissolving the already
formed porous silicon layer ($m_{3}$), to obtain the porosity as 
$p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.}
The porosity of the layers was obtained by a previous calibration
curve through a gravimetric technique \cite{Pap2006} 
\notaV{Si es que se adjunta (further details see supplementary
information), sino ya se ha mencionado en otros articulos}. The 
etching rate of PS was obtained by synthetizing single layers under 
similar conditions and measuring their thicknesses through Scanning 
Electron Microscopy (SEM). Absolute reflectivity measurements were 
carried out with a Perkin Elmer Lambda 950 UV/Visible 
spectrophotometer with a variable angle universal reflectance 
accessory (URA) for different incident angles $\theta _{i}=10^{\circ 
}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and 
$60^{\circ }$ using non-polarized light. The maximum and minimum 
values of $\theta _{i}$ were constrained by the angular range of the 
equipment accessory URA.
